---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(lmerTest)
library(brms)
library(ggbeeswarm)
```

## Background

### The *swarm* construction

## Experiments

### The *swarm* construction

TODO document and visualize subject exclusion criteria

```{r}
swarm_df.04 <- read_csv("../04_comprehension_swarm-full/merged_df.csv")
swarm_df.09 <- read_csv("../09_comprehension_swarm-full-nonalternating-control/merged_df.csv")
swarm_df <- bind_rows(swarm_df.04, swarm_df.09) %>% 
  filter(
    # Exclude practice and filler trials.
    !condition_0 %in% c("practice", "filler"),
    
    # Exclude trials from control experiment.
    !is_nonalternating_control,
    
    # Exclude trials on which subjects refused to answer.
    !slider_copout,
    
    # Retain only concrete items.
    `A concrete?`) %>% 
  mutate(
    # Switch coding to make model interpretation a little more intuitive (both
    # main effects should point in the same direction).
    location_is_subject = !agent_is_subject,
    
    # Scale slider_value to range on (0, 1) in order to be compatible with
    # beta regression model.
    slider_value = (0.001 + slider_value) / 100.002)

glimpse(swarm_df)
```

```{r}
# Sum-code all logical variables.
contrasts(swarm_df$location_is_subject) = c(-1, 1)
contrasts(swarm_df$agent_is_given) = c(-1, 1)
```

#### Model fits

```{r}
# Fit a mixed-effects linear regression with maximal random effect structure.
swarm_model.linear <- 
  lmer(slider_value ~
       agent_is_given * location_is_subject +
       (agent_is_given * location_is_subject|item_id) + 
       (agent_is_given * location_is_subject|uniqueid),
       data=swarm_df,
      control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=100000)))
```
```{r}
summary(swarm_model.linear)
```



```{r}
# Fit a mixed-effects beta regression with maximal random effect structure.
swarm_model <- brm(slider_value ~
                   agent_is_given * location_is_subject + 
                   (agent_is_given * location_is_subject|item_id) + 
                   (agent_is_given * location_is_subject|uniqueid),
                 data=swarm_df, family="beta", chains=4)
```

```{r}
summary(swarm_model)
```

#### Visualizations

##### Plot raw results, but subtracting random effects

```{r}
# Predict random effects for each observation.
# NB brms doesn't support making posterior predictions with ranefs only. So
# I'm lazily using linear model's estimates for now instead, for this
# visualization.
swarm_ranef_obs = predict(swarm_model.linear, random.only=T)

swarm_df_controlled = swarm_df %>% 
  cbind(swarm_ranef_obs) %>% 
  mutate(slider_value_ranef_normed = slider_value - swarm_ranef_obs)

swarm_df_controlled %>%
  ggplot(aes(x=location_is_subject, y=slider_value_ranef_normed, color=agent_is_given)) +
  geom_boxplot() +
  geom_quasirandom(dodge.width=0.75, alpha=0.3) +
  
  ggtitle("Slider responses, normalized using random effect estimates") +
  labs(y="Normalized slider value")
```


##### Conditional effects plots

Plot posterior predictive for slider responses conditioned on construction and givenness. Does not incorporate random effects.
Uncertainty over response computed by combining the 95% posterior confidence interval estimates for each variable.

```{r}
# brms::conditional_effects(model.09.main.brm, effects="agent_is_subject:agent_is_given", conditions=data.frame(agent_is_concrete=c(F, T)), ask=F, points=T)

interactions::cat_plot(swarm_model, geom="line", y.label="Slider response value (0–1)",
                       pred=location_is_subject, pred.values=c(FALSE, TRUE), pred.labels=c("A\n(Bees are swarming)", "L\n(The garden is swarming)"), x.label="Construction",
                       modx=agent_is_given, modx.values=c(FALSE, TRUE), modx.labels=c("L (The garden)", "A (Bees)"), legend.main="Given entity")
```