---
title: "R Notebook"
output: html_notebook
---

This notebook contains some exploratory data analysis on the Switchboard dative alternation dataset. This analysis was used to design naturalistic items exhibiting the dative alternation.

```{r}
library(tidyverse)
library(languageR)
```

```{r}
data(dative)
glimpse(dative)
```

## Materials filtering

We're only interested in verbs which have attested uses in both constructions.

```{r}
valid_verbs <- dative %>%
  group_by(Verb) %>% 
    count(RealizationOfRecipient) %>% 
    pivot_wider(names_from=RealizationOfRecipient, values_from=n) %>% 
    drop_na() %>%
  select(Verb)

sub_dative <- semi_join(dative, valid_verbs)
```


## Q1: When are pronominal arguments attested/preferred?

Different verbs have different strengths of preference for pronominal arguments. It's important to see attested examples of non-pronominal arguments in both constructions -- otherwise we might be building an unacceptable sentence for one half of the alternation.

### By verb: proportion of ditransitives with pronominal recipients

```{r}
sub_dative %>% 
  filter(RealizationOfRecipient == "NP") %>% 
  group_by(Verb) %>% 
    count(PronomOfRec, .drop=FALSE) %>% 
  group_by(Verb) %>% mutate(total_attested=sum(n)) %>% filter(total_attested > 0) %>% 
  mutate(proportion_rec_pronominal=prop.table(n)) %>% 
  filter(PronomOfRec == "pronominal") %>% 
  select(Verb, n, proportion_rec_pronominal) %>% 
  arrange(-proportion_rec_pronominal)
```

### By verb: proportion of PPs with pronominal themes

```{r}
sub_dative %>% 
  filter(RealizationOfRecipient == "PP") %>% 
  group_by(Verb) %>% 
    count(PronomOfTheme, .drop=FALSE) %>% 
  group_by(Verb) %>% mutate(total_attested=sum(n)) %>% filter(total_attested > 0) %>% 
  mutate(proportion_theme_pronominal=prop.table(n)) %>%
  filter(PronomOfTheme == "pronominal") %>% 
  select(Verb, total_attested, proportion_theme_pronominal) %>% 
  arrange(-proportion_theme_pronominal)
```
