---
title: "R Notebook"
output: html_notebook
---

## Preliminaries

```{r}
library(tidyverse)
library(lme4)
library(lmerTest)
library(ggbeeswarm)
```

```{r}
df <- read_csv(
  "merged_df.csv",
  col_types = list(
    uniqueid = col_factor()
  ))
glimpse(df)
```

```{r}
filtered_df <- df %>%
  filter(!slider_copout, 
         !(condition_0 %in% c("practice", "filler")),
         !is_nonalternating_control) %>% 
  mutate(agent_is_concrete=`A concrete?`,
         location_is_subject=!agent_is_subject)
```

## Main regression

```{r}
# contr.sum with logical variables makes FALSE = 1, TRUE = -1, which is confusing.
contrasts(filtered_df$location_is_subject) = c(-1, 1)
contrasts(filtered_df$agent_is_given) = c(-1, 1)
contrasts(filtered_df$agent_is_concrete) = c(-1, 1)
```


```{r}
model.09.main <-
  lmer(slider_value ~
       agent_is_concrete * agent_is_given * location_is_subject +
       (agent_is_given * location_is_subject|item_id) + 
       (agent_is_concrete * agent_is_given * location_is_subject|uniqueid),
       data=filtered_df,
      control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=100000)))
summary(model.09.main)
```


### Bayesian
```{r}
library(brms)
```

```{r}
filtered_df_trans <- filtered_df %>% 
  mutate(slider_value = (slider_value + 0.1) / 100.2)
model.09.main.brm <- brm(slider_value ~
                   agent_is_concrete * agent_is_given * location_is_subject + 
                   (agent_is_given * location_is_subject|item_id) + 
                   (agent_is_concrete * agent_is_given * location_is_subject|uniqueid),
                 data=filtered_df_trans, family="beta",
                 chains=4)
```
```{r}
summary(model.09.main.brm)
```
## Visualizations

### Plot raw results, but subtracting random effects

```{r}
# Predict random effects for each observation.
ranef_obs = predict(model.09.main, random.only=T)

filtered_df_controlled = filtered_df %>% 
  cbind(ranef_obs) %>% 
  mutate(slider_value_ranef_normed = slider_value - ranef_obs)

filtered_df_controlled %>%
  ggplot(aes(x=agent_is_concrete, y=slider_value_ranef_normed, color=agent_is_given)) +
  geom_boxplot() +
  geom_quasirandom(dodge.width=0.75, alpha=0.3)
```


### Conditional effects plots

Plot posterior predictive for slider responses conditioned on concreteness, construction, and givenness. Does not incorporate random effects.
Uncertainty over response computed by combining the 95% posterior confidence interval estimates for each variable.

```{r}
# brms::conditional_effects(model.09.main.brm, effects="agent_is_subject:agent_is_given", conditions=data.frame(agent_is_concrete=c(F, T)), ask=F, points=T)

# interactions::cat_plot(model.09.main.brm, geom="line", y.label="Slider response value (0--1)",
#                        pred=agent_is_subject, pred.values=c(TRUE, FALSE), pred.labels=c("A", "L"), x.label="Construction",
#                        modx=agent_is_given, modx.values=c(TRUE, FALSE), modx.labels=c("A", "L"), legend.main="Given",
#                        mod2=agent_is_concrete, mod2.values=c(FALSE, TRUE), mod2.labels=c("Abstract agent", "Concrete agent"))

interactions::cat_plot(model.09.main.brm, geom="line", y.label="Slider response value (0–1)",
                       pred=location_is_subject, pred.values=c(TRUE, FALSE), pred.labels=c("L\n(The garden is swarming)", "A\n(Bees are swarming)"), x.label="Construction",
                       modx=agent_is_given, modx.values=c(TRUE, FALSE), modx.labels=c("A (Bees)", "L (The garden)"), legend.main="Given entity",
                       mod2=agent_is_concrete, mod2.values=c(FALSE, TRUE), mod2.labels=c("Abstract agent", "Concrete agent"))
ggsave("catplot_slider_concreteness-givenness-construction.png")
```

## Control analysis with non-alternating verbs


```{r}
control_df <- df %>%
  filter(is_nonalternating_control,
         !slider_copout, 
         !(condition_0 %in% c("practice", "filler"))) %>% 
  mutate(agent_is_concrete=`A concrete?`,
         location_is_subject=!agent_is_subject)
```

```{r}
# Check: how much data per item--condition?
control_df %>% group_by(AV, condition_0) %>% summarise(n=n()) %>% arrange(n)
```


```{r}
# contr.sum with logical variables makes FALSE = 1, TRUE = -1, which is confusing.
contrasts(control_df$agent_is_given) = c(-1, 1)
contrasts(control_df$agent_is_concrete) = c(-1, 1)
```


```{r}
model.09.control <-
  lmer(slider_value ~
                agent_is_concrete * agent_is_given +
                (agent_is_given|item_id) + 
                (agent_is_concrete * agent_is_given|uniqueid),
              data=control_df,
              control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=100000)))
summary(model.09.control)
```


## Fishing

```{r}
filtered_df_trans <- filtered_df %>% 
  mutate(slider_value = (slider_value + 0.1) / 100.2) %>% 
  filter(agent_is_concrete == TRUE)
model.09.concrete.brm <- brm(slider_value ~
                   agent_is_given * location_is_subject + 
                   (agent_is_given * location_is_subject|item_id) + 
                   (agent_is_given * location_is_subject|uniqueid),
                 data=filtered_df_trans, family="beta",
                 chains=4)
```

```{r}
summary(model.09.concrete.brm)
```

```{r}
concrete_df <- filtered_df %>% filter(agent_is_concrete == T)
model.09.concrete <- lmer(slider_value ~
                agent_is_given * location_is_subject +
                (agent_is_given * location_is_subject|item_id) + 
                (agent_is_given * location_is_subject|uniqueid),
              data=concrete_df,
              control=lmerControl(optimizer="bobyqa", optCtrl=list(maxfun=100000)))
summary(model.09.concrete)
```

```{r}
ranef_obs_concrete = predict(model.09.concrete, random.only=T)

filtered_df_concrete_controlled = concrete_df %>% 
  cbind(ranef_obs_concrete) %>% 
  mutate(slider_value_ranef_normed = slider_value - ranef_obs_concrete)

filtered_df_concrete_controlled %>%
  ggplot(aes(x=location_is_subject, y=slider_value_ranef_normed, color=agent_is_given)) +
  geom_boxplot() +
  geom_quasirandom(dodge.width=0.75, alpha=0.3)
```

